\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{graphicx}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage[english]{babel}
\usepackage[parfill]{parskip}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{float}
\usepackage{tikz}
\usetikzlibrary{automata, positioning}
\begin{document}

\section*{Solutions exercises Queuing Theory and Simulation}

\textbf{Go to \url{https://github.com/Anton-4/queuing-exercises} to get the most recent version of this document}

I found that the solutions written down in class often missed steps, important details and explanations, which is why I have created this document with detailed,
annotated and complete solutions for most exercises.

If certain solutions are unclear or new exercises are given please create issues or contribute to the github repository so that we can maintain this document over the years.

This document was based on notes by ir. Mathias De Brouwer and ir. Anton Van Moere, \LaTeX created by Anton Van Moere.
Help in understanding and expanding solutions was provided by ir. Alexander Erreygers and dr. Sarah Dendievel.
Course was given by Professor Dieter Fiems and Professor. ir. Joris Walraevens.

\input{prob_refresh.tex}

\input{markov.tex}

\input{BDQ.tex}

\input{wait_delay.tex}

\input{MVA.tex}

\input{transform_analysis.tex}

\input{inversion_PGF_LST.tex}

\input{queue_nets.tex}

\input{simulation.tex}


\end{document}
